---
title: 'Statistical report: Complications pregnancy'
subtitle: 'DRAFT'
author: 'Statistician: Lina Benson'
  
date: "`r Sys.Date()`"
output:
  pdf_document:
    fig_caption: yes
    fig_height: 7
    fig_width: 7
    number_sections: yes
link-citations: yes
bibliography: references.bib
nocite: '@*'
header-includes:
   - \usepackage{draftwatermark}
---

\newpage 
\tableofcontents 
\listoftables
\listoffigures
\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, include = TRUE, comment = "",
  warning = FALSE, message = FALSE, fig.pos = "H",
  fig.path = "../output/figs/"
)
options(knitr.kable.NA = "")
```

```{r adjust_directory_if_needed, include=FALSE}
# Uncomment lines below if rmd file is placed in a subdirectory
knitr::opts_knit$set(root.dir = normalizePath("../"))
```

```{r load_project}
# 1. Set options in config/global.dcf
# 2. Load packages listed in config/global.dcf
# 3. Import functions and code in lib directory

ProjectTemplate::reload.project()

cacheon <- FALSE
```             

# Data handling

## Data source

File used: IMPROVED cleaned 20210421.xlsx. 

No selection criteria applied. OK? For the neonatal outcomes Intrauterine fetal death are excluded. 

# Statistical analysis 

## General

All analyses were performed using `r sessionInfo()$R.version$version.string` [@r]. 
The level of significance is set to 5%, two-sided. No adjustment for multiple 
comparisons were made and therefore the results should be viewed with some care.

## Missing data

The amount of missing data is small. Therefore the risk of bias due to missing 
data is negligible and no imputation is performed and all analysis are performed 
on complete case analysis. Except for income. Therefore a sensitivity analysis is performed excluding income? Imputation?

## Baseline characteristics

```{r, child = "../src/tab1.Rmd"}

```

## Association with pregnancy outcomes

```{r, child = "../src/outdesk.Rmd"}

```

The association between the socioeconomic covariates and the respective pregnancy 
outcomes were investigated using a logistic regression model for the binary outcomes 
and a proportional odds model for the outcomes with > 2 levels. 

```{r, child = "../src/outcome.Rmd"}

```

### Assumptions

To do: Outliers were investigated with Cook's distance and multicollinearity 
with the variance inflation factor. 
The continuous variables were checked for linearity using splines. Proportional odds assumption was assessed... 
=> Action...???. 

\clearpage
\newpage

# Reproducibility

## R session information {#sessioninfo}

```{r sessinfo}
sessionInfo()
```

## R code

The R code for all data handling and statistical analyses are found: 
https://github.com/KIHeartFailure/pregcomplications. On publication
the repository will be made public so as to 
link to it from the resulting article for increased transparency and code sharing.
No data or output is stored in the repository. 

# References
